DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-25 paper/evaluation.tex
Update cache mapping and relevant section

In order to determine if the DNN is mostly affected by shared DRAM 
contention, we partition the L2 cache of the Pi3 and reperform the 
same experiments to see if there are any noticable changes. For the 
partition, we employ PALLOC~\cite{yun2014rtas}, a color-based page 
allocator that works on the kernel level. For the bit mask, we select 
bits 12, 13 and 14 as those bits are used to specifically access the 
shared L2 cache, as can be seen by \ref{fig:cache-mapping}. This 
results in 2\textsuperscript{3} = 8 colors, which we then assign to the Pi3's 
physical cores such that each core has two unique colors (colors 0 
and 1 are assigned to core 0, colors 2 and 3 are assigned to core 1, 
etc.).

@@

The results can be seen in Figures \ref{fig:palloc_multicore} - 
\ref{fig:palloc_bandwidth_l2missrate}. As 
expected, based off of previous results, we find that the performance 
of the DNN remains consistent when cache partitioning is employed. 
When fewer cores are used, DNN performance is slightly affected as 
the entire L2 cache isn't available to the network. In the case of 
running multiple models simultaneously, no performance improvements 
are seen, which further shows that the shared cache has no affect on 
the DNN's real-time performance.

@@

By partitioning the shared L2 cache, we find that no noticable 
improvements are gained and that performance remains consistent, or 
decreases, depending on the circumstances. As a result, we find that 
cache partitioning is not an effective isolation mechanism, and that 
the performance of the shared DRAM is of greater importance to the 
real-time efficiacy of the DeepPicar.

@@

Lastly, we find that partitioning the shared L2 cache provides 
practically no benefits to the real-time performance of the DNN. To the 
contrary, performance is negatively affected when fewer cores are used, 
due to less cache being available, and memory intensive co-runners are 
introduced, as they generate more memory contention. Furthermore, we 
find that performance remains consistent when multiple models are run 
simultaneously. As such, we conclude that the shared L2 cache is not 
important to the DNN's real-time performance.

>>>>

In order to determine if the DNN is mostly affected by shared DRAM 
contention, we partition the L2 cache of the Pi3 and reperform the 
same experiments to see if there are any noticable changes. For the 
partition, we employ PALLOC~\cite{yun2014rtas}, a color-based page 
allocator that works on the kernel level. For the bit mask, we select 
bits 12, 13 and 14 as they can be used to access the L2 cache,
as can be seen by \ref{fig:cache-mapping}. This results in 
2\textsuperscript{3} = 8 colors, which we then assign to the Pi3's 
physical cores such that each core has two unique colors (colors 0 
and 1 are assigned to core 0, colors 2 and 3 are assigned to core 1, 
etc.). In the case of bit 12, since we use 2 colors for each partition,
the L1D cache is not partitioned in our experiments.

@@

The results can be seen in Figures \ref{fig:palloc_multicore} - 
\ref{fig:palloc_bandwidth_l2missrate}. As 
expected, based off of previous results, we find that the performance 
of the DNN remains consistent when cache partitioning is employed. 
When fewer cores are used, DNN performance is slightly affected as 
the entire L2 cache isn't available to the network. In the case of 
running multiple models simultaneously, no performance improvements 
are seen, which further shows that the shared cache has little affect on 
the DNN's real-time performance.

@@

By partitioning the shared L2 cache, we find that no noticable 
improvements are gained and that performance remains consistent, or 
decreases, depending on the circumstances. As a result, we conclude that 
cache partitioning is not an effective isolation mechanism, and that 
the performance of the shared DRAM is of greater importance to the 
real-time efficiacy of the DeepPicar.

@@

Lastly, we find that partitioning the shared L2 cache provides 
practically no benefits to the real-time performance of the DNN. To the 
contrary, performance is negatively affected when fewer cores are used, 
due to less cache being available, and memory intensive co-runners are 
introduced, as they generate more memory contention. Furthermore, we 
find that performance remains consistent when multiple models are run 
simultaneously. As such, we conclude that the shared L2 cache is not 
essential to the DNN's real-time performance.
